### 2022-09-21 main/chapter_context.tex
add mt bhadron footnote

Sensitivity to hadronic momenta is crucial,
both directly to measure heavy hadronic decays
(like $t \rightarrow bq\bar{q}$),
and indirectly for the missing transverse momenta from semi-invisible
leptonic decays (like $W \to \ell\nu$).
Since individual hadron identities are less relevant to these measurements,%
\footnote{%
Rare decays like
$W^\pm\rightarrow \pi^\pm \gamma$ or $W^\pm\rightarrow \pi^\pm \pi^+ \pi^-$
could give clean signals, but are not competitive due to their
tiny production rates and difficult identification~\cite{
cdf1996search,
mangano2014wpiy,
cms2021wpiy
}.%
}
it makes sense for \atlas' design to forfeit hadron identification systems
in favour of precise calorimetry with total angular coverage.

>>>>

Sensitivity to hadronic momenta is crucial,
both directly to measure heavy hadronic decays
(like $t \to bq\bar{q}$),
and indirectly for the missing transverse momenta from semi-invisible
leptonic decays (like $W \to \ell\nu$).
Since individual hadron identities are less relevant to these measurements,%
\footnote{%
Rare decays like
$W^\pm \to \pi^\pm \gamma$ or $W^\pm \to \pi^\pm \pi^+ \pi^-$
could give clean signals, but are not competitive due to their
tiny production rates and difficult identification~\cite{
cdf1996search,
mangano2014wpiy,
cms2021wpiy
}.%
Leptonic $B$ hadron decays are useful in $m(t)$ measurements, but these
do not require hadron reconstruction~\cite{
CDF:2009mbf,
CMS:2016ixg,
ATLAS:2022jbw
}.%
}
it makes sense for \atlas' design to forfeit hadron identification systems
in favour of precise calorimetry with total angular coverage.
